---
title: "vignette_soilmech"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette_soilmech}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(soilmech)
```

This R package contains many functions to create charts related to soil mechanics and foundation design, or to demonstrate key concepts.


# Particle size distributions

To create an empty particle size distribution chart:
```{r, fig.dim = c(7, 3.5)}
ggplot_psdchart()
```

Data traces can be added (use `add_points == TRUE` to also add the data points). x-axis may be trimmed as necessary:
```{r, fig.dim = c(7, 3.5)}
ggplot_psdchart(
  trace_diameter = rep(c(0.01, 0.1, 1), 2),
  trace_passing = c(0.2, 0.5, 0.9, 0.1, 0.3, 0.6),
  trace_group = rep(c("A", "B"), each = 3),
  add_points = TRUE,
  legend_position = "right",
  xlim = c(0.002, 2)
)
```

You can hightlight specifc points on a single trace using crosshairs:
```{r, fig.dim = c(7, 3.5)}
ggplot_psdchart(
  trace_diameter = c(0.002, 0.01, 0.03, 0.1, 0.3, 1, 10),
  trace_passing = c(0.05, 0.1, 0.3, 0.5, 0.6, 0.7, 0.9),
  crosshairs_diameter = c(0.01, 0.1),
  crosshairs_passing = c(0.1, 0.5),
  crosshairs_group = c("D[10]==0.01~mm", "D[50]==0.10~mm"),
  crosshairs_parse = TRUE
)
```
